How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-17 tse-paper/content.tex
add more details to study design, relates to #41

In summary, this literature study shows the need for build log
analysis techniques that are build-environment agnostic, automated
and can be configured with small effort.
We achieve this by developing three techniques for which the
information to be retrieved is specified through examples or keywords.

@@

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:blirt}
In this article, we evaluate different techniques to automatically
retrieve pieces of information that appear literally in the build
logs.
%, i.e., techniques that do not aggregate, combine, or deducted
%information.
We call such pieces of information from build logs
\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
The techniques we investigate here do not require a formal lexer and
parser to analyze the entire structure of build logs, but focus on
ad-hoc extracting just one specific piece of information per
configuration.

@@

@@

% TODO Caro: redo
\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
  clip]{img/study.pdf}
	\caption{Design of our technique comparison study.}
	\label{fig:study}
\end{figure*}

To investigate which technique is best suited to retrieve chunks from
CI build logs we evaluate the three chunk retrieval techniques
PBE, CTS and KWS.
Random Line Retrieval (RLR), acts as a baseline for
the comparison.
The following section
describes our study design and which metrics we measure to answer our
research questions.
In the presentation of the results, we first focus
on each of the three techniques and later compare them against each
other.

\subsection{LogChunks}
For this study we created the previously published data set
\emph{LogChunks}.
It encompasses 797 build logs from Travis CI,
stemming from a broad range of 80 GitHub repositories and 29
programming languages.
For each file, the authors manually ``labeled
the log part (chunk) describing why the build
failed''~\cite{brandt2020logchunks}.
We include keywords, which we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks are surrounded by the same markings
within the log we assign them the same structural category.

% We run four techniques on the examples from \emph{LogChunks}.

\noindent
\textbf{Training and Test Set}
% TODO Moritz: You said: Add details how key words were extracted.
% Add example?
% how the keywords were put in logchunks does not fit here, that is
% maybe answered 2 paragraphs above already?
% how KWS uses the keywords is already described in the section
% introducing the technique => I would scrap everything but the first
% sentence directly above here :)

% TODO Moritz: You said: Add more details.
% How was the split in numbers?
% this is described in the following paragraph, should we merge them
% (bc there are also no sub-RQs now) or is it close enough? :)
For each repository in \emph{LogChunks}, we split the examples
chronologically into training and test set.
Therefore, we train on
examples from past build logs and test on more recent build logs.

\noindent % TODO: adapt if we change the research questions
\textbf{RQ 2.1: Size of Training and Test Set}
We evaluate the techniques with different training set
sizes, to analyze how many examples the chunk retrieval techniques need to
perform best.
We train each technique with one to five examples from each of
the repositories within \emph{LogChunks}.
The size of the test set is one.

\noindent
\textbf{RQ 2.2: Recording Structural Categories}
We record the structural categories
of the examples in the training and test sets, to determine how
structurally similar the examples for the chunk
retrieval techniques need to be.

\noindent
\textbf{RQ2.3: Accuracy Metrics}
we save the output lines of the chunk retrieval run on the input
of the test example ($\mathit{RetrievedLines}$), to measure the
accuracy of the retrieved chunks
As oracle in our evaluation, we save the
desired lines from the output of the test example
($\mathit{DesiredLines}$).

We calculate and define a number of metrics for the context of our
evaluation.

@@

	% What about when a line is replicated twice?
	% I.e., Are line numbers part of this? => no.
	% not checked, but if lines are identical they also contain
	% the same information so if someone asks we can defend I think
	\item $\mbox{Precision} = \dfrac{|\mathit{True\
	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
	Precision of a chunk retrieval describes which proportion of
	the retrieved lines were actually desired.

	\item $\mbox{Recall} =
	\dfrac{|\mathit{True\ Positives}|}{|\mathit{DesiredLines}|}$
	\vspace{0.2cm} \\
	Recall of a chunk retrieval describes which proportion of the
	desired lines were retrieved.
	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
	\vspace{0.2cm}\\
	In addition, we calculate the F$_{1}$-score, the harmonic mean
	of precision and recall.
We prefer F$_{1}$ to other aggregate
	measures such as accuracy because for a
	``needle-in-the-haystack'' scenario, we do not want to bloat
	our results by correctly not finding lots of irrelevant log
	lines.
	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
	We define a successful retrieval as one where all desired
	lines were
	extracted, therefore when recall is one.
\end{itemize}

>>>>

In summary, this literature study shows the need for build log
analysis techniques that are build-environment agnostic, automated
and can be configured by the user with little effort.
We achieve this by developing three techniques for which the
information to be retrieved is specified through examples or keywords.

@@

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:crt-characteristics}
In this article, we evaluate different techniques to automatically
retrieve pieces of information that appear literally in the build
logs.
%, i.e., techniques that do not aggregate, combine, or deducted
%information.
We call such pieces of information from build logs
\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
The techniques we investigate here do not require a formal lexer and
parser to analyze the entire structure of build logs, but focus on
ad-hoc extracting just one specific piece of information per
configuration.

@@

To investigate when our chunk retrieval techniques are suited to
analyze build logs (\textbf{RQ2}), we perform an empirical comparison
study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
In particular we are interested in how many examples a technique
should be trained with for best performance (\textbf{RQ2.1}),
how similar the structural representation of the targeted log chunks
has to be (\textbf{RQ2.2}) and how reliable the quality of the
produced outputs are (\textbf{RQ2.3}).

@@

In the following we present the data set we created for this study,
our study process (presented in \Cref{fig:study}) and the metrics
we measure to answer our research questions.

\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
  clip]{img/study.pdf}
	\caption{Design of our technique comparison study.}
	\label{fig:study}
\end{figure*}

\subsection{LogChunks}
For this study we created the previously published data set
\emph{LogChunks}.
It encompasses 797 build logs from Travis CI,
stemming from a broad range of 80 GitHub repositories and 29
programming languages.
For each file, the authors manually ``labeled
the log part (chunk) describing why the build
failed''~\cite{brandt2020logchunks}.
We included keywords, which we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks were surrounded by the same markings
within the log we assigned them the same structural category.

\subsection{Study Process}
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---end therefore the
same build environment (1).
One to five examples make up the training set (2).
We vary its size to measure how many examples are needed to
confidently configure a technique.
The training set is so small, because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a training set size of 1, as users of our techniques
should receive reliable results on every build log they analyze.
As a next step, we configure the chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
\begin{itemize}
  \item The size of training set (\textbf{RQ2.1}),
  \item the number of structural categories in the training set
  (\textbf{RQ2.2})
  \item the lines of the retrieval output ($\mathit{RetrievedLines}$),
  and our oracle, the output defined in the test example
  ($\mathit{DesiredLines}$).
  From these we calculate accuracy metrics (\textbf{RQ2.1}).
\end{itemize}

\textbf{Accuracy Metrics}
We calculate a number of accuracy metrics to measure how well
the chunk retrieval techniques perform in our evaluation:

@@

	% What about when a line is replicated twice?
	% I.e., Are line numbers part of this? => no.
	% not checked, but if lines are identical they also contain
	% the same information so if someone asks we can defend I think

	\item $\mbox{Precision} = \dfrac{|\mathit{True\
	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
	Precision of a chunk retrieval describes which proportion of
	the retrieved lines were actually desired.

	\item $\mbox{Recall} =
	\dfrac{|\mathit{True\ Positives}|}{|\mathit{DesiredLines}|}$
	\vspace{0.2cm} \\
	Recall of a chunk retrieval describes which proportion of the
	desired lines were retrieved.

	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
	\vspace{0.2cm}\\
	In addition, we calculate the F$_{1}$-score, the harmonic mean
	of precision and recall.
  We prefer F$_{1}$ to other aggregate
	measures such as accuracy because for a
	``needle-in-the-haystack'' scenario, we want to avoid bloating
	our results by correctly not finding lots of irrelevant log
	lines.

	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
	\mathit{Recall} = 1, \mathit{false\ otherwise}$ \vspace{0.05cm}\\
	We define a successful retrieval as one where all desired
	lines were
	extracted, therefore when recall is one.
\end{itemize}

This concludes one execution within our evaluation.
We conduct one run for each of the four chunk retrieval techniques,
for each of the eighty repositories in \emph{LogChunks} (8)
and for each of the five training set sizes (2).
In total we perform 1600 runs, 400 for each of the chunk retrieval
techniques PBE, CTS, KWS and RLR.

Our implementation of the techniques, as well as our evaluation
harness and the code we used to process our results is offered
for inspection and reproduction in our replication package
~\cite{brandt2020chunk-replication}.
